Geometric Control for Autonomous Landing on Asteroids

### 2017-08-07 manuscript.tex
Add an example of feature matching
Show a picture of features on asteroid itokawa
Add more detail on SE(3) controller

In order to determine the attitude control input, we first define a desired attitude tracking command.
An arbitrary smooth attitude tracking command \( R_d (t) \in \SO \) is given as a function of time.
The corresponding angular velocity command is obtained using the attitude kinematics equation, \( \hat{\Omega}_d = R_d^T \dot{R}_d \).
With the desired attitude command, we then define the errors associated with the attitude and angular velocity.
The attitude and angular velocity tracking errors must be careful chosen to remain on the tangent bundle of \SO.
First, an attitude error function is defined on \( \SO \times \SO \) as
\begin{align}\label{eq:attitude_error_function}
    \Psi(R, R_d) = \frac{1}{2} \tr{I - R_d^T R}.
\end{align}
This locally positive definite function parameterizes the error between the current attitude, \( R \), and the desired attitude command \( R_d \).
Using the variations of \( \Psi \) gives the attitude tracking error vector \( e_R \in \R^3 \) as
\begin{align}\label{eq:attitude_error_vector}
    e_R = \frac{1}{2} \parenth{R_d^T R - R^T R_d^\vee}.
\end{align}
After further manipulation and the attitude kinematics equation it is possible to define the angular veloicty tracking error \( e_\Omega \in \R^3 \) as
\begin{align}\label{eq:angular_velocity_error_vector}
    e_\Omega = \Omega - R^T R_d \Omega_d .
\end{align}

@@

\section{Numerical Simulation}\label{sec:simulation}

>>>>

In order to determine the attitude control input, we first define a desired attitude tracking command.
An arbitrary smooth attitude tracking command \( R_d (t) \in \SO \) is given as a function of time.
The corresponding angular velocity command is obtained using the attitude kinematics equation, \( \hat{\Omega}_d = R_d^T \dot{R}_d \).
With the desired attitude command, we then define the errors associated with the attitude and angular velocity.
The attitude and angular velocity tracking errors must be careful chosen to remain on the tangent bundle of \SO.
First, an attitude error function is defined on \( \SO \times \SO \) as
\begin{align}\label{eq:attitude_error_function}
    \Psi(R, R_d) = \frac{1}{2} \tr{I - R_d^T R}.
\end{align}
This locally positive definite function parameterizes the error between the current attitude, \( R \), and the desired attitude command \( R_d \).
Using the variations of \( \Psi \) gives the attitude tracking error vector \( e_R \in \R^3 \) as
\begin{align}\label{eq:attitude_error_vector}
    e_R = \frac{1}{2} \parenth{R_d^T R - R^T R_d^\vee}.
\end{align}
After further manipulation and the attitude kinematics equation it is possible to define the angular veloicty tracking error \( e_\Omega \in \R^3 \) as
\begin{align}\label{eq:angular_velocity_error_vector}
    e_\Omega = \Omega - R^T R_d \Omega_d .
\end{align}
With the properly defined attitude error vectors the rotational control input is defined as 
\begin{align*}
    \vb{u}_m = - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - J \parenth{\hat{\Omega} R^T R_d \Omega_d - R^T R_d \dot{\Omega}_d} - \vb{M}_1 - \vb{M_2} 
\end{align*}
where \( k_R, k_\Omega \) are positive controller constants.

The translational control input is defined in a similar manner. 
First we define a smooth tracking command \( x_d(t) \in \R^3 \), which defines the desired position of the spacecraft in the inertial frame.
The tracking error vectors are easier to define as they evolve on a Euclidean space rather than a nonlinear manifold and are given by
\begin{align}
    e_x = x - x_d ,\\
    e_v = v - \dot{x}_d .
\end{align}
With the error variables, the translational control input is then given by
\begin{align}
    \vb{u}_f = - k_x e_x  - k_v e_v + ( m_1  + m_2 ) \ddot{x}_d - \vb{F}_1 - \vb{F}_2 ,
\end{align}
where \( k_x, k_v \) are positive constants.

@@

\subsection{Estimating motion from Monocular Imagery}\label{eq:image_processing}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/itokawa_feature_matching.png}
    \caption{Demonstration of feature detection and matching between simulated images of asteroid 25413 Itokawa}
    \label{fig:itokawa_feature_matching}
\end{figure}
\section{Numerical Simulation}\label{sec:simulation}
